---
title: "simpleRegress"
author: "Karen Gomez"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

We are going to compute Regression models; finding one regression model that does the best job in predicting the bear length and its correspondence to the bear's neck size, age, head length, and head with. We have to choose which one is the best.

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Whichever has the largest adjusted r square is the best model. The adjusted R square for this model, LENGTH~NECK, is 0.75.

## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

The order from worst to best is LENGTH~AGE (0.51), LENGTH~HEADWTH (0.53), LENGTH~WEIGHT (0.74), LENGTH~CHEST (0.79), LENGTH~HEADLEN (0.84).

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R square for this model, LENGTH~HEADLEN, is 0.84.

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R square for this model, LENGTH~CHEST, is 0.79.

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R square for this model, LENGTH~WEIGHT, is 0.74.

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R square for this model, LENGTH~HEADWTH, is 0.53.

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R square for this model, LENGTH~AGE, is 0.51.

### Conclusion/Discussion

Based on the graphs, the worst to best models are LENGTH~AGE (0.51), LENGTH~HEADWTH (0.53), LENGTH~WEIGHT (0.74), LENGTH~CHEST (0.79), LENGTH~HEADLEN (0.84). Which means, according to all the models we utilized, the model with the biggest Adjusted R Squared is always the best, therefore, LENGTH~HEADLEN (0.84) is the best model out of all.





